### 2017-01-26 manuscript.rmd
added url for compara gene trees

	# Name of the compara gene trees file
	gene_tree_name = "Compara.75.protein.nhx.emf"

>>>>

	# Name of the compara gene trees file. This is from 
	# ftp://ftp.ensembl.org/pub/release-75/emf/ensembl-compara/homologies/
	# but not included here due to its size. Put it in the kmrr/ directory
	gene_tree_name = "Compara.75.protein.nhx.emf"
